---
title: "Algorithms"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Algorithmss}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ZeitreihenR)
library(ggplot2)
library(tibble)
```

## Introduction

In this vignette, we will explain the algorithms of the **TimeSeries** package in R. The algorithms are used to analyse time series and make predictions and are based on the book *Introduction to Time-Series Analysis and Forecasting* by Peter J. Brockwell and Richard A. Davis. This vignette contains examples and explanations for the following methods:

-   Auto Covariance Function **sampleACVF**
-   Durbin Levinson Algorithm **DLA** and the algorithm with predictions **DL_predictions**
-   Innovations Algorithm **innovations_step** and the algorithm with predictions **innovations_predictor**
-   Spectral Density function **spectral_density**
-   Periodogram for time series **periodogram**

### Auto Covariance Function

The auto covariance function is a function which describes the dependencies between a time series at a time difference h: (TODO: bessere beschreibung einsetzen ) Let $X_t$ be a stationary time series. The *autocovariance function (ACVF)* of $X_t$ at lag h is $$\gamma_X(h) = Cov(X_t+h, X_t)$$. This function however only works if the underlying model is known. For that reason, we will work with the following sample autocovariance function, that uses the data: The *sample autocovariance function* is $$\hat{\gamma}(h) = \frac{1}{n}\sum_{t=1}^{n-|h|}(x_{t+|h|}-\bar{x})(x_t-\bar{x}), -n < h < n$$. The *SACVF* is a realization of the definition and computes the sample autocovariance function of a time series at a given point of time.

#### Example SACVF

Consider a time series ar_ts with parameter 0.5 and start value 1.


```{r}
ar_ts <- AR(ar_params = 0.5, start_values = 1, n = 50, sd = 1)
plot_timeseries(ar_ts)
plot_SACVF(ar_ts)

```

### Durbin Levinson Algorithm

The Durbin Levinson algorithm is a algorithm used for predictions of a time series. The underlying definition is based on Definition 2.5.3 of *Introduction to Time-Series Analysis and Forecasting* by Peter J. Brockwell and Richard A. Davis.

The *DLA* method is used to predict a specified number of $\phi_i$. Based on the *DLA*, the *DL_predictor* method then makes predictions for a time series.

#### Example: Durbin Levinson with prediction

```{r}
ar_ts <- AR(ar_params = 0.5, start_values = 1, n = 10, sd = 1)
plot_timeseries(ar_ts)
dl_pred <- DL_predictor(ar_ts, pred_len=10, entire_ts = FALSE)
plot_timeseries(dl_pred)
```

### Innovations Algorithm

The Innovations algorithm is another algorithm used for predictions of a time series. The underlying definition is based on Definition 2.5.4 of *Introduction to Time-Series Analysis and Forecasting* by Peter J. Brockwell and Richard A. Davis.

The *innovations_step* method is used to predict a specified number of $\theta_i$. Based on the *innovations_step* method, the *innovations_predictor* method then makes predictions for a time series.

#### Example: Innovations algorithm with prediction

```{r}
ma_ts <- MA(ma_params = 0.5, n = 20, sd = 1)
plot_timeseries(ma_ts)
ma_pred <- innovations_predictor(ma_ts, pred_len=10, entire_ts = FALSE)
plot_timeseries(ma_pred)
```

### Spectral density

The spectral density describes how the variance of a stationary time series is distributed over different frequencies, the total integrated spectral density equalling the variance of the series. The spectral density is a helpful tool in identifying domiant frequencies and periodicities in the data.

The spectral density function implented here is based on *Introduction to Time-Series Analysis and Forecasting* by Peter J. Brockwell and Richard A. Davis. The general definition is given in Definition 4.1.1, and the specific definition here used to calculate the spectral density for AR and MA processes is given in Definition 4.4.1.

#### Example of the Spectral Density

Below, AR(1) and MA(1) processes are created, and their respective spectral densities are computed. Both are then evaluated at the frequency 0.1. Lastly, both spectral densities are plotted for all frequencies in the range from 0 to 0.5.

```{r}
AR1  <- AR(ar_params = c(0.3), start_values = c(0), n = 100, sd = 1)
MA1 <- MA(ma_params = c(0.9),sd = 1,n = 100)

f <- spectral_density(AR1)
g <- spectral_density(MA1)

f(0.1)
g(0.1)

plot_spectral_density(AR1)
plot_spectral_density(MA1)
```
### Periodogram

The periodogram of a time series is a estimator of the spectral density of the time series. For a time series $X_1,...X_n$ it is defined as: $$ I_n(\lambda)=\frac{1}{n} \Bigg\| \sum \limits\*{t=1}^{n}x\_{t}e^{-it\*\lambda} \Bigg\| \^2 $$ where $x_t$ is a combination of trigonometric functions containing Fourier frequencies. The *periodogram* method is a implementation of the periodogram algorithm in Definition 4.2.1 of the book *Introduction to Time-Series Analysis and Forecasting* by Peter J. Brockwell and Richard A. Davis. It takes a TimeSeries object and returns the Fourier-frequencies as well as the estimated spectral density values.

### Example periodogram

```{r}
ar_time_series <- AR(start_values = c(1, 1), ar_params = c(0.6, 0.6), sd = 1, n = 100)
periodogram(ar_time_series)
plot_periodogram(ar_time_series)
```
