---
title: "Visualizations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Visualizations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ZeitreihenR)
library(ggplot2)
library(tibble)
library(patchwork)
```

## Introduction

In this vignette we provide an overview over the visualization methods provided in the **TimeSeries** package.

-   *plot_timeseries* method to visualize a TimeSeries object

-   *plot_SACVF* method to visualize the SACVF or SACF of a TimeSeries object

-   *plot_spectral_density* method to visualize the spectral density of a AR/MA-TimeSeries object
-   *plot_periodogram* method to visualize the periodogram of a TimeSeries object

-   *plot_ts_overview* method to visualize all of the above in a composition plot.

### Plots of Timeseries

The *plot_timeseries* method provides plots for a given time series. Additionally, it can also include predictions of a time series, such as made by the *Durbin Levinson* or the *Innovations* algorithm.

#### Examples for timeseries plots

We start with an example of an AR TimeSeries without prediction.

```{r}
ar_time_series <- AR(start_values = c(1, 1), ar_params = c(0.6, 0.6), sd = 1, n = 100)
plot_timeseries(ar_time_series)
```

In order to plot a time series with prediction, one must first use one of the prediction algorithms and then use the plot_timeseries function with the additional argument *prd*:

```{r}
ma_time_series <- MA(ma_params=c(0.6,0.6), n=100)
plot_timeseries(ma_time_series)
ma_pred <- DL_predictor(ma_time_series,pred_len = 5,entire_ts = FALSE)
plot_timeseries(ma_time_series, prd=ma_pred)


```

### Plots of SACVF/SACF

The *plot_SACVF* method provides SACVF/SACF for a given time series. 

#### Examples for timeseries plots

We start with an example of the SACVF of an AR TimeSeries.

```{r}
ar_time_series <- AR(start_values = c(1, 1), ar_params = c(0.6, 0.6), sd = 1, n = 100)
plot_SACVF(ar_time_series,max_lag=25,acf=FALSE)
```

The argument *max_lag* defines the maximum lag up to which we will compute the functions. The logical argument *acf* defines if we want to plot the SACF instead of the SACVF:

```{r}
ar_time_series <- AR(start_values = c(1, 1), ar_params = c(0.6, 0.6), sd = 1, n = 100)
plot_SACVF(ar_time_series,max_lag=25,acf=TRUE)
```

### Plots of Spectral Density

The *plot_spectral_density* method provides plots of the spectral density of a given AR or MA time-series.

#### Examples for spectral density plots

In order to plot a spectral density, one simply puts an AR or MA object into the *plot_spectral_density* function, as in the following example:

```{r}
ar_time_series <- AR(start_values = c(1, 1), ar_params = c(0.7, -0.3), sd = 1, n = 100)
plot_spectral_density(ar_time_series)
ma_time_series <- MA(ma_params = c(0.4,-0.7), n = 100)
plot_spectral_density(ma_time_series)
```

One can also choose the number of points n to be plotted (default 10^3):

```{r}
AR1  <- AR(ar_params = c(0.3), start_values = c(0), n = 100, sd = 1)
plot_spectral_density(ar_time_series, n = 10)
```



### Plots of Periodogram

The *plot_periodogram* method provides plots of the periodogram of a given time series.

#### Examples for periodogram plots

In order to plot a periodogram, one simply puts a TimeSeries object into the *plot_periodogram* function, as in the following example:

```{r}
ar_time_series <- AR(start_values = c(1, 1), ar_params = c(0.6, 0.6), sd = 1, n = 100)
plot_periodogram(ar_time_series)
ma_time_series <- MA(ma_params = c(1,-0.9), n = 100)
plot_periodogram(ma_time_series)
```

### Composition Plots
The *plot_ts_overview* method provides an overview of a given time_series object using the library **patchwork**. It consists of *plot_timeseries*, *plot_SACVF*, *plot_spectral_density* (if possible) and *plot_periodogram*. The layout is automatically chosen depending on the availability of the spectral density.


#### Examples for composition plots


```{r}
ar_time_series <- AR(start_values = c(1, 1), ar_params = c(0.6, 0.6), sd = 1, n = 100)
vec <- 1:10
vec_ts <- as(vec,"TimeSeries")
plot_ts_overview(ar_time_series)
plot_ts_overview(vec_ts)
```
