---
title: "Visualizations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Visualizations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ZeitreihenR)
library(ggplot2)
library(tibble)
```

## Introduction

In this vignette we provide an overview over the visualization methods provided in the **TimeSeries** package.

-   *plot_timeseries* method to visualize a TimeSeries object

-   *plot_periodogram* method to visualize the periodogram of a TimeSeries object

### Plots of Timeseries

The *plot_timeseries* method provides plots for a given time series. Additionally, it can also include predictions of a time series, such as made by the *Durbin Levinson* or the *Innovations* algorithm.

#### Examples for timeseries plots

We start with an example of an AR TimeSeries without prediction.

```{r}
ar_time_series <- AR(start_values = c(1, 1), ar_params = c(0.6, 0.6), sd = 1, n = 100)
plot_timeseries(ar_time_series)
```

In order to plot a time series with prediction, one must first use one of the prediction algorithms and then use the plot_timeseries function with the additional argument *prd*:

```{r}
ar_time_series <- AR(start_values = c(1, 1), ar_params = c(0.6, 0.6), sd = 1, n = 100)
plot_timeseries(ar_time_series)
ar_pred <- DL_predictor(ar_time_series, pred_len=10, entire_ts = FALSE)
plot_timeseries(ar_time_series, prd=ar_pred)

```

### Plots of Periodogram

The *plot_periodogram* method provides plots of the periodogram of a given time series.

#### Examples for periodogram plots

In order to plot a periodogram, one simply puts a TimeSeries object into the *plot_periodogram* function, as in the following example:

```{r}
ar_time_series <- AR(start_values = c(1, 1), ar_params = c(0.6, 0.6), sd = 1, n = 100)
plot_periodogram(ar_time_series)
ma_time_series <- MA(ma_params = c(1,-0.9), n = 100)
plot_periodogram(ma_time_series)
```
